---
title: "Grouped progress"
output: html_document
editor_options: 
  chunk_output_type: console
params:
  input_DF: DF_analysis$DF_analysis
  last_scale: "Goodbye_DIRt"
  goal: 100
  group_vars: ""
  n_groups: 1
---

```{r setup, include=FALSE}

# DEBUG
# targets::tar_load(DF_analysis)
# params = list(
#   input_DF = DF_analysis$DF_analysis,
#   last_scale = "Goodbye_DIRt",
#   goal = 500,
#   group_vars = c("DEMOGR_genero_DIRd"),
#   n_groups = 5
# )



knitr::opts_chunk$set(echo = TRUE)

# Check if group_vars columns exist
if (all(params$group_vars %in% names(params$input_DF))) {
  
  # General data prepatation
  DF_analysis = 
    params$input_DF %>% 
    select(all_of(params$group_vars), params$last_scale) %>% 
    filter(!is.na(params$last_scale)) %>% 
    count(across(all_of(params$group_vars)), name = "completed") %>% 
    mutate(missing = (params$goal / params$n_groups) - completed,
           goal = (params$goal / params$n_groups)) 
    
    # Specific variable transformation 
    # mutate(AIM_DIRt = 
    #          case_when(
    #           AIM_DIRt %in% c("d", "e") ~ "EXP",
    #           AIM_DIRt %in% c("c2", "c3") ~ "CONc",
    #           AIM_DIRt %in% c("c1a", "c1b", "ab") ~ "CONa",
    #           TRUE ~ NA_character_)) %>% 
  
    # rename(group = AIM_DIRt)
} else {
  cli::cli_alert_danger("group_vars NOT in DF_analysis")
}




```

---  


`r nrow(params$input_DF)` out of `r params$goal` participants completed the experiment (`r round(nrow(params$input_DF) / params$goal, 2) * 100`%). The completion criteria is reaching `r params$last_scale`.  

The final goal (`r params$goal`) is divided in `r params$n_groups` groups.  This is `r (params$goal / params$n_groups)` per group.   

We create the groups crossing the variables: `r paste(params$group_vars, collapse = " & ")`.  

---  

```{r summary, echo=FALSE}

if (all(params$group_vars %in% names(DF_analysis))) {
  
  DT_analysis = 
    DF_analysis %>% 
    DT::datatable(options = list(dom = 'ti'), rownames = FALSE) 


  DT_analysis %>% 
    DT::formatStyle(
      columns = c("missing"), 
      target = "cell",
      color = DT::styleInterval(cuts = c(-10, 0), values = c("red", "orange", "green"))
  )
  
} else {
  
  cat("group_vars NOT in DF_analysis. Fix in _targets.R")
  
}

```
