---
title: "Candidatos"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
df_FORM_RAW = read_rds(here::here(".vault/output/data/df_FORM5.rds"))
df_Status_RAW = read_rds(here::here(".vault/output/data/df_FORM6.rds"))
df_AIM = read_rds(here::here(".vault/output/data/df_AIM.rds")) %>% select(RUT, AIM_DIRt)

# df_FORM_RAW; df_Status_RAW; df_AIM
```

## Summary

```{r summary, include=FALSE}

# Read main df_FORM_RAW contains everyone that filled the form. 
# In run_sensitive_data is joined by SDG (id/RUT). Only the ones that completed the experiment have id.

DF = 
  df_FORM_RAW %>% 
  left_join(df_AIM, by = "RUT") %>% 
  select(id, RUT, AIM_DIRt, FORM5_02_DIR, FORM5_03_DIR, FORM5_04_DIR, FORM5_05_DIR, FORM5_06_DIR, FORM5_07_DIR, FORM5_08_DIR) %>% 
  
  rename(
    email = FORM5_02_DIR, 
    name = FORM5_03_DIR,
    edad = FORM5_04_DIR,
    sexo = FORM5_05_DIR,
    years_education = FORM5_06_DIR,
    comuna = FORM5_07_DIR,
    telefono = FORM5_08_DIR
    ) %>% 
  
  mutate(grupo = 
           case_when(
            AIM_DIRt == "d" | AIM_DIRt == "e" ~ "EXP",
            AIM_DIRt == "c2" | AIM_DIRt == "c3" ~ "CONc",
            AIM_DIRt == "c1a" | AIM_DIRt == "c1b" | AIM_DIRt == "ab" ~ "CONa",
            TRUE ~ NA_character_),

         edad = 
           case_when(
             between(edad, 25, 33) ~ "25-33",
             between(edad, 34, 42) ~ "34-42",
             between(edad, 43, 50) ~ "43-50",
             edad < 25 ~ "demasiado joven",
             edad > 50 ~ "demasiado viejo"),
         
         completed = 
           case_when(
             is.na(id) ~ "CALL",
             TRUE ~ "OK")
         ) %>% 
  
  # Filter out by age, sex and socioeconomic group
  filter(sexo != "No binario") %>%
  filter(edad != "demasiado viejo" & edad != "demasiado joven") %>% 
  drop_na(grupo) %>% 
  
  select(id, RUT, completed, edad, sexo, grupo, edad, telefono, email, name, comuna)



table_done_temp =
  DF %>% 
  select(-RUT) %>% 
  count(grupo, completed, edad, sexo) %>% 
  mutate(grupo = paste0(grupo, "_", completed)) %>% 
  select(-completed) %>% 
  pivot_wider(names_from = grupo, values_from = n) #, names_prefix = "n_"


# If we don't have certain types of people, create columns
cols = c(CONc_CALL = 0, CONa_CALL = 0, EXP_CALL = 0, CONc_OK = 0, CONa_OK = 0, EXP_OK = 0)
table_done_temp = tibble::add_column(table_done_temp, !!!cols[setdiff(names(cols), names(table_done_temp))]) 

# If table is empty, create it
if (nrow(table_done_temp) == 0) table_done_temp = tibble(edad = NA_character_, sexo = NA_character_, CONc_CALL = 0, CONa_CALL = 0,  EXP_CALL = 0,  CONc_OK = 0,  CONa_OK = 0,  EXP_OK = 0)
  
# Vulnerable group: groups d y e 50% of sample
# Non-vulnerable group: groups c3 y c2 25% of sample
# Non-vulnerable group: groups ab, c1a y c1b 25% of sample
  
table_done = 
  table_done_temp %>% 
  complete(sexo = c("Masculino", "Femenino")) %>% 
  complete(edad = c("25-33", "34-42", "43-50"), nesting(sexo)) %>% 
  drop_na(edad, sexo) %>% 
  replace_na(list(CONc_CALL = 0, CONa_CALL = 0, EXP_CALL = 0, CONc_OK = 0, CONa_OK = 0, EXP_OK = 0)) %>% 
  mutate(GOAL_CONa = (CONa_OK - 20),
         GOAL_CONc = (CONc_OK - 20),
         GOAL_EXP = (EXP_OK - 40)) %>% 
         # DIFF_CONEXP = EXP_OK - (CONa_OK + CONc_OK)
         # DIFF_CONaCONc = (CONa_OK - CONc_OK)
         # MARGEN_EXP = GOAL_EXP + n_EXP_CALL,
         # MARGEN_CON = GOAL_CON + n_CON_CALL) %>% 
         # Candidatos = ) 
  select(edad, sexo, CONa_OK, CONc_OK, EXP_OK, GOAL_CONa, GOAL_CONc, GOAL_EXP,	CONa_CALL, CONc_CALL, EXP_CALL) %>% 
  select(-matches("NA_", ignore.case = FALSE))

```
   
  
```{r summary-table, echo=FALSE}

DT::datatable(table_done, options = list(dom = 'ti'), rownames = FALSE) %>% 
      DT::formatStyle(
        columns = c("GOAL_CONa", "GOAL_CONc", "GOAL_EXP"), 
        target = "cell",
        color = DT::styleInterval(cuts = c(-10, 0), values = c("red", "orange", "green"))
    )

```
**CON_OK**: Grupo control completados; **EXP_OK**: Grupo experimental completados  
**GOAL_CON**: Cuantos faltan del grupo control; **GOAL_EXP**: Cuantos faltan del grupo experimental    
**CON_CALL**: Grupo control esperando llamada; **EXP_CALL**: Grupo experimental esperando llamada  

- EXP: Vulnerable group: groups d y e 50% of sample
- CONa: Non-vulnerable group: groups c3 y c2 25% of sample
- CONc: Non-vulnerable group: groups ab, c1a y c1b 25% of sample

---   

### Candidatos

Actualizar STATUS de Candidatos aqui: [http://cscn.uai.cl/lab/public/instruments/protocols/6/](http://cscn.uai.cl/lab/public/instruments/protocols/6/){target="_blank"}

```{r candidatos-table, echo=FALSE}

df_Status =
  df_Status_RAW %>%
  mutate(date = as.Date(datetime)) %>% 
  group_by(RUT) %>% 
  summarise(status = paste(paste0("[", date, "]: ", FORM6_01_RAW), collapse = ", "),
         notes =  paste(paste0("[", date, "]: ", FORM6_02_RAW), collapse = ", "), 
         .groups = "keep")

table_candidatos_long =
  DF %>% 
  left_join(df_Status, by = "RUT") %>% 
  filter(completed == "CALL") %>% 
  drop_na(edad) %>% 
  select(grupo, edad, sexo, RUT, name, telefono, email, comuna, status, notes)

DT::datatable(table_candidatos_long, filter = 'top', 
              options = list(
                dom = 'tip',
                # autoWidth = TRUE,
  columnDefs = list(list(width = '300px', targets = c("status", "notes")))))

```



---   


### Completados

Participantes que han completado el protocolo:  

```{r completed-table, echo=FALSE}
DF_completed = 
  DF %>% 
  filter(completed == "OK") %>% 
  select(-completed)

DT::datatable(DF_completed, filter = 'top', 
              options = list(
                dom = 'tip',
                autoWidth = TRUE))
```
