---
title: "Candidatos"
output: html_document
editor_options: 
  chunk_output_type: console
---

## TODO
- ADD table with mean age by group and sex to be able to check how biased the groups are.


```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
df_FORM_RAW = read_rds(here::here(".vault/data/df_FORM_RAW.rds"))
df_AIM = read_rds(here::here(".vault/data/df_AIM.rds")) %>% select(RUT, AIM_DIRt)
```

## Summary

```{r summary, include=FALSE}

# df_FORM_RAW contains everyone that filled the form. Only the ones that completed the experiment have id.

DF = 
  df_FORM_RAW %>% 
  left_join(df_AIM, by = "RUT") %>% 
  select(id, AIM_DIRt, FORM_emaild_DIRd, FORM_name_DIRd, FORM_age_DIRd, FORM_sex_DIRd, FORM_years_education_DIRd, FORM_comuna_DIRd, FORM_telefono_DIRd) %>% 
  rename(
    email = FORM_emaild_DIRd, 
    name = FORM_name_DIRd,
    edad = FORM_age_DIRd,
    sexo = FORM_sex_DIRd,
    years_education = FORM_years_education_DIRd,
    comuna = FORM_comuna_DIRd,
    telefono = FORM_telefono_DIRd
    ) %>% 
  
  mutate(grupo = 
           case_when(
            AIM_DIRt == "d" | AIM_DIRt == "e" ~ "EXP",
            AIM_DIRt == "c2" | AIM_DIRt == "c3" ~ "CONc",
            AIM_DIRt == "c1a" | AIM_DIRt == "c1b" | AIM_DIRt == "ab" ~ "CONa",
            TRUE ~ NA_character_
            ),

         edad = 
           case_when(
             between(edad, 25, 33) ~ "25-33",
             between(edad, 34, 42) ~ "34-42",
             between(edad, 43, 50) ~ "43-50",
             edad < 25 ~ "demasiado joven",
             edad > 50 ~ "demasiado viejo",
           ),
         
         completed = 
           case_when(
             is.na(id) ~ "CALL",
             TRUE ~ "OK"
           )
         ) %>% 
  filter(sexo != 2) %>%
  filter(edad != "demasiado viejo" & edad != "demasiado joven") %>% 
  select(id, completed, edad, sexo, grupo, edad, telefono, email, name, comuna)



table_done_temp =
  DF %>% 
  count(grupo, completed, edad, sexo) %>% 
  mutate(grupo = paste0(grupo, "_", completed)) %>% 
  select(-completed) %>% 
  pivot_wider(names_from = grupo, values_from = n) #, names_prefix = "n_"


# If we don't have certain types of people, create columns
cols = c(CONc_CALL = 0, CONa_CALL = 0, EXP_CALL = 0, CONc_OK = 0, CONa_OK = 0, EXP_OK = 0)
table_done_temp = tibble::add_column(table_done_temp, !!!cols[setdiff(names(cols), names(table_done_temp))]) 
  
# Vulnerable group: groups d y e 50% of sample
# Non-vulnerable group: groups c3 y c2 25% of sample
# Non-vulnerable group: groups ab, c1a y c1b 25% of sample
  
table_done = 
  table_done_temp %>% 
  complete(edad = c("25-33", "34-42", "43-50"), nesting(sexo)) %>% 
  replace_na(list(CONc_CALL = 0, CONa_CALL = 0, EXP_CALL = 0, CONc_OK = 0, CONa_OK = 0, EXP_OK = 0)) %>% 
  mutate(GOAL_CONa = (CONa_OK - 20),
         GOAL_CONc = (CONc_OK - 20),
         GOAL_EXP = (EXP_OK - 40)) %>% 
         # DIFF_CONEXP = EXP_OK - (CONa_OK + CONc_OK)
         # DIFF_CONaCONc = (CONa_OK - CONc_OK)
         # MARGEN_EXP = GOAL_EXP + n_EXP_CALL,
         # MARGEN_CON = GOAL_CON + n_CON_CALL) %>% 
         # Candidatos = ) 
  select(edad, sexo, matches("OK"), matches("GOAL"), matches("CALL"))

```


### DONE

```{r echo=FALSE}
knitr::kable(table_done)
```
**CON_OK**: Grupo control completados; **EXP_OK**: Grupo experimental completados  
**CON_CALL**: Grupo control esperando llamada; **EXP_CALL**: Grupo experimental esperando llamada  
**GOAL_CON**: Cuantos faltan del grupo control; **GOAL_EXP**: Cuantos faltan del grupo experimental    


### Candidatos

```{r summary-table, echo=FALSE}

# table_candidatos = 
#   DF %>% 
#   filter(completed == 0) %>% 
#   drop_na(edad) %>% 
#   count(grupo, edad, sexo)
#   
# knitr::kable(table_candidatos)

table_candidatos_long = 
  DF %>% 
  filter(completed == "CALL") %>% 
  drop_na(edad) %>% 
  select(grupo, edad, sexo, name, telefono, email, comuna)

DT::datatable(table_candidatos_long, filter = 'top', options = list(dom = 'tip'))

```
