---
title: "Grouped progress"
output: html_document
editor_options: 
  chunk_output_type: console
params:
  input_DF: DF_analysis
  last_scale: "Goodbye_DIRt"
  goal: 100
  group_vars: ""
  n_groups: 1
---

```{r setup, include=FALSE}

# DEBUG
# targets::tar_load(DF_analysis)
# params = list(
#   input_DF = DF_analysis,
#   last_scale = "DEBRIEF_esfuerzo_DIRd",
#   goal = 300,
#   group_vars = c("AIM_DIRt", "DEMOGR_genero_DIRd"),
#   n_groups = 6
# )


knitr::opts_chunk$set(echo = TRUE)


# General data prepatation
DF_analysis = 
  params$input_DF %>% 
  select(all_of(params$group_vars), params$last_scale) %>% 
  filter(!is.na(params$last_scale)) %>% 
  count(across(all_of(params$group_vars)), name = "completed") %>% 
  mutate(missing = (params$goal / params$n_groups) - completed,
         goal = (params$goal / params$n_groups)) 
  
  # Specific variable transformation 
  # mutate(AIM_DIRt = 
  #          case_when(
  #           AIM_DIRt %in% c("d", "e") ~ "EXP",
  #           AIM_DIRt %in% c("c2", "c3") ~ "CONc",
  #           AIM_DIRt %in% c("c1a", "c1b", "ab") ~ "CONa",
  #           TRUE ~ NA_character_)) %>% 
  # rename(group = AIM_DIRt)

```

---  


`r nrow(DF_analysis)` out of `r params$goal` participants completed the experiment (`r round(nrow(DF_analysis) / params$goal, 2) * 100`%). The completion criteria is reaching `r params$last_scale`.  

The final goal (`r params$goal`) is divided in `r params$n_groups` groups.  This is `r (params$goal / params$n_groups)` per group.   

We create the groups crossing the variables: `r paste(params$group_vars, collapse = " & ")`.  

---  

```{r summary, echo=FALSE}

DF_analysis %>% 
DT::datatable(options = list(dom = 'ti'), rownames = FALSE) %>% 
      DT::formatStyle(
        columns = c("missing"), 
        target = "cell",
        color = DT::styleInterval(cuts = c(-10, 0), values = c("red", "orange", "green"))
    )


```
