---
title: "Codebook"
output: 
  html_document: 
    toc: yes
editor_options: 
  chunk_output_type: console
params:
  last_task: ""
  pid_report: 0

---

```{r setup, include=FALSE}
# DEBUG
# source(here::here("_packages.R"))
# DF_clean = read_rds(here::here("_targets/objects/DF_clean"))
# DF_raw = read_rds(here::here("_targets/objects/DF_raw"))
# params = list(
#   pid_report = 0,
#   last_task = "Goodbye"
# )

knitr::opts_chunk$set(echo = TRUE)
targets::tar_load(DF_clean)
targets::tar_load(DF_raw)
DF = DF_clean

```

```{r plot_form_progress, include=FALSE}
  
plot_form_progress = show_progress_pid(pid = params$pid_report, files_vector = DF_clean$filename, last_task = "Goodbye", goal = 500)$PLOT_progress

ggsave(here::here("outputs/plots/plot_form_progress.png"), plot_form_progress, width = 15, height = 9)
  
```


## Summary {.tabset}

```{r summary, include=FALSE}

number_participants = DF_raw %>% distinct(id) %>% nrow()

number_tasks = DF_raw %>% distinct(experimento) %>% nrow()

text_participants = 
  DF_raw %>% 
  count(id, experimento) %>% 
  count(id, name = "tasks") %>% 
  count(tasks, name = "people") %>% 
  arrange(desc(tasks))


```

### Tasks and participants
We had a total of `r number_participants` participants completing up to `r number_tasks` different tasks.   

```{r summary-table1, echo=FALSE}
DT::datatable(text_participants,
              width = "50%",
              rownames = FALSE,
              options = list(dom = 't',
                             pageLength = 20))
```

---  

### By participant  

```{r summary-table, echo=FALSE}

all_tasks = DF_raw %>% distinct(experimento) %>% pull(experimento)

summary_table = 
  DF_raw %>% 
    select(id, experimento, time_elapsed) %>% 
    group_by(id, experimento) %>% 
    summarise(TIME = round(max(time_elapsed)/60000, 2), 
              N = n(), 
              .groups = "keep") %>% 
    group_by(id) %>% 
    summarise(TIME = sum(TIME), 
              N = n(), 
              tasks = paste(experimento, collapse = ", "),
              .groups = "keep") %>% 
      mutate(missing = paste(all_tasks[!all_tasks %in% (strsplit(tasks, split = ", ") %>% unlist())], collapse = ", "))

DT::datatable(summary_table, filter = 'top', options = list(dom = 'ltip', pageLength = 10))
  
```


### By task  

```{r summary-table2, echo=FALSE}

summary_table2 =
  DF_raw %>% 
    group_by(id, experimento) %>% 
    summarise(
      n_participants = n_distinct(id),
      time = max(time_elapsed) / 60000,
      .groups = "drop"
    ) %>% #View
  
    group_by(experimento) %>% 
    summarise(
      n_participants = n(),
      mean_time = round(mean(time), 1),
      time_elapsed_min = round(min(time), 1),
      time_elapsed_max = round(max(time), 1),
      .groups = "keep"
    )
 
DT::datatable(summary_table2, filter = 'top', options = list(dom = 'ltip', pageLength = 10))

```


### By task and participant 

```{r summary-table3, echo=FALSE}

summary_table3 =
  DF_raw %>% 
    group_by(id, experimento) %>% 
    summarise(
      # n_participants = n_distinct(id),
      time = round(max(time_elapsed) / 60000, 2),
      .groups = "drop"
    ) 

DT::datatable(summary_table3, filter = 'top', options = list(dom = 'ltip', pageLength = 10))
```


### Order of tasks

```{r summary-position, echo=FALSE}
summary_position = DF_raw %>% 
  distinct(id, experimento, datetime) %>% 
  group_by(id) %>% 
  arrange(id, (datetime)) %>% 
  mutate(Order = row_number()) %>% 
  select(-datetime) %>% 
  group_by(experimento) %>% 
  summarise(MEAN_Position = round(mean(Order), 1),
            SD_Position = round(sd(Order), 1),
            MIN_Position = min(Order), 
            MAX_Position = max(Order), 
            .groups = "drop") %>% 
  arrange(MEAN_Position, experimento)

DT::datatable(summary_position, filter = 'top', options = list(dom = 'ltip', pageLength = 10))

```



## Details of tasks {.tabset}

### Number of items per task

```{r echo=FALSE}

# Alternative trialid for each scale
trialid_table = DF %>% 
  filter(trial_type != "fullscreen") %>% 
  select(experimento, trial_type, trialid, response) %>% 
  group_by(experimento) %>% 
  distinct(trialid) %>% 
  count(experimento, name = "number_items")


DT::datatable(trialid_table, 
              filter = 'top', 
              options = list(dom = 'ltip', 
                             pageLength = 15))

```


### Trialid's and questions for each of the tasks:  



```{r echo=FALSE}

# trialid and question_text for each experiment
trialid_detail_table = DF %>% 
  select(experimento, trialid, stimulus) %>% 
  group_by(experimento) %>% 
  distinct(trialid, stimulus) 


DT::datatable(trialid_detail_table, 
              filter = 'top', 
              options = list(dom = 'ltip', 
                             pageLength = 15))

```


### Responses (numeric and categorical)

Only showing multi-choice, slider and liker scales.  


```{r echo=FALSE}

# Alternatives responses for each scale
responses_table = DF %>% 
  # distinct(trial_type)
  select(experimento, trial_type, trialid, response) %>% 
  filter(trial_type %in% c("survey-multi-choice-vertical", "survey-multi-choice-horizontal", "likert", "html-slider-response")) %>% 
  group_by(experimento) %>% 
  distinct(trialid, response) 


DT::datatable(responses_table, 
              filter = 'top', 
              options = list(dom = 'ltip', 
                             pageLength = 15))


```


<!-- ### All Responses -->


```{r echo=FALSE}
#   DF_responses =
#     DF %>%
#     count(trialid, experimento, responses) %>%
#     group_by(experimento, trialid) %>%
#     summarise(N = n(),
#               Responses = paste(responses, collapse = ", "),
#               .groups = "drop") %>%
#     group_by(experimento, Responses) %>%
#     summarise(N = n(),
#               trialid = paste(trialid, collapse = ", "),
#               .groups = "drop") %>% 
#   select(experimento, trialid, Responses, N)
# 
# 
# DT::datatable(DF_responses, 
#               filter = 'top', 
#               options = list(dom = 'ltip', 
#                              pageLength = 15))

```

